\subsection{Used technologies}
%------------------------------------------
\subsubsection{JUNG library}
For creation and representation of graphs and coefficients calculations JUNG library~\cite{jung} has been used.
JUNG(Java Universal Network/Graph Framework) is a software library that provides a common and extendible language for modeling, analysis, and visualization of data that can be represented as a graph or network.

JUNG's \emph{DirectedSparseGraph} has been used as a class being the container for datasets' data.
Datasets' instances has been wrapped in custom \emph{Node} class, having a list of floating point values which were then used for distance calculations.


%------------------------------------------
\subsubsection{Distance algorithm}
For distance algorithm, indicating distance between \emph{Node}s, Euclidean distance algorithm has been implemented.
All values from \emph{Node}'s values list has been squared, summed and then square root of tham sum has been calculated.
The difference between this values of nodes has been used to determine distances between \emph{Node}s.


%------------------------------------------
\subsubsection{Pearson correlation coefficient}
For Pearson correlation coefficient calcalation a class from Apache Common Math library~\cite{apache_common_math} -\emph{org.apache.commons.math3.stat.correlation.PearsonsCorrelation} - has been used.

In this method for each link in the graph we take in-degrees from both of its ends - source node's in-degree and  destination node's in-degree - and then save it in 2 arrays.
After the whole graph has been processed those arrays are then fed to \emph{PearsonsCorrelation} class and the coefficient is calculated with \emph{correlation} method.

\begin{filecode}[label=lst:pearsonCorrelation,caption=Method used for Pearson correlation coefficient calculation.]
  \lstinputlisting{./code/pearsonCorrelation.java}
\end{filecode}

%------------------------------------------
\subsection{Implemented solution}
Implemented solution is a \emph{jar} file with following usage (replace \emph{VERSION} with appropriate version of the \emph{jar} file in possession).

\shellcmd{java -jar knngraphs-VERSION.jar -k K file1.csv [file2.csv ...]}

One can state one or more files (datasets) as shown above which will be used to create kNN graphs, show them and calculate Pearson coefficient vs K graph for each file(dataset).
After launch, user will be asked until what parameter $K$ he wants the program to calculate the graphs (it will start its calcaulations from 1) if it has not been passes in as command line parameter.
After that one can choose whether to show kNN graph for each K ( Warning: it may be RAM and CPU heavy to show graphs for many $K$s) and whether to save Pearson coefficient vs $K$ graph to \emph{.svg} file in the working directory.

Implemented solution's source code has been push onto github repository~\footnote{Patryk Małek, kNN graphs, (2014), GitHub repository,~\url{https://github.com/pmalek/knngraphs}}.